---
# Supported options: 
#   sn-nature:       Style for submissions to Nature Portfolio journals
#   sn-basic:        Basic Springer Nature Reference Style/Chemistry Reference Style
#   sn-mathphys:     Math and Physical Sciences Reference Style
#   sn-aps:          American Physical Society (APS) Reference Style
#   sn-vancouver:    Vancouver Reference Style
#   sn-apa:          APA Reference Style 
#   sn-chicago:      Chicago-based Humanities Reference Style
#   default:         Default

classoptions: 
  - sn-basic      
  # - Numbered      # Optional: Use numbered references instead of namedate references (only for sn-nature, sn-basic, sn-vancouver, sn-chicago, sn-mathphys or sn-nature)
  # - referee       # Optional: Use double line spacing 
  # - lineno        # Optional: Add line numbers
  # - iicol         # Optional: Double column layour
  
# TAG submission guidelines: https://link.springer.com/journal/122/submission-guidelines

title: "Impact of pedigree depth in the Australian strawberry breeding program: variance component estimation, prediction accuracies and estimation of clonal and breeding values"
titlerunning: "Pedigree depth in the Australian strawberry breeding program"

authors: 
  - prefix: Dr.
    firstname: Ky
    lastname: Mathews
    degrees: PhD
    email: ky.mathews@daf.qld.gov.au
    affiliation: [1]
    corresponding: TRUE
    #equalcont: These authors contributed equally to this work.
    
  - prefix: Dr.
    firstname: Katie
    lastname: O'Connor
    degrees: PhD
    email: katie.oconnor@daf.qld.gov.au
    affiliation: [1]
    
  - prefix: Dr.
    firstname: Jodi
    lastname: Neal
    degrees: PhD
    email: Jodi.Neal@daf.qld.gov.au
    affiliation: [1]


affiliations:
  - number: 1
    corresponding: TRUE
    info:
      orgdiv: Department of Primary Industries
      orgname: Queensland Government
    address:
        street: Maroochy Research Facility, 47 Mayers Road
        city: Nambour
        postcode: 4560
        state: Queensland
        country: Australia
    
  
keywords: # 4-6
  - A matrix
  - relatedness
  - yield

abstract: |
  Key message: Less than 30 words summarising the main achievement.

  Abstract should be around 200 words.

bibliography: bibliography.bib

header-includes: |
  %% Per the spinger doc, new theorem styles can be included using built in style, 
  %% but it seems the don't work so commented below
  %\theoremstyle{thmstyleone}%
  \newtheorem{theorem}{Theorem}%  meant for continuous numbers
  %%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
  %% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
  \newtheorem{proposition}[theorem]{Proposition}%
  %%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.

  %% \theoremstyle{thmstyletwo}%
  \theoremstyle{remark}
  \newtheorem{example}{Example}%
  \newtheorem{remark}{Remark}%

  %% \theoremstyle{thmstylethree}%
  \theoremstyle{definition}
  \newtheorem{definition}{Definition}%

output: 
  bookdown::pdf_book:
    base_format: rticles::springer_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      out.extra = "")  # This forces knitr to label all figures.
```

# Introduction {#sec:intro}

```{r secintro, child = c('Sections/1-Introduction.Rmd')}
```

# Materials and methods {#sec:meth}

```{r secmeth, child = c('Sections/2-Methods.Rmd')}
```

# Results {#sec:res}

```{r secres, child = c('Sections/3-Results.Rmd')}
```

# Discussion {#sec:disc}

```{r secdisc, child = c('Sections/4-Discussion.Rmd')}
```

# Conclusions

We found...

\backmatter

\bmhead{Supplementary information}

If your article has accompanying supplementary file/s please state so here.

\bmhead{Acknowledgments}

The authors thank present and past members of the Australian Strawberry Breeding Program and staff at the Maroochy Research Facility for the involvement in field preparation and maintenance, plant propagation, plant maintenance, fruit harvesting and processing, data collection, etc etc. 

# Declarations {.unnumbered}

## Funding
The Australian Strawberry Breeding Program has been funded by Hort Innovation using the strawberry research and development levy, with co-contributions from the Queensland Government through its Department of Primary Industries and funds from the Australian Government.

## Competing Interestions
The authors have no relevant financial or non-financial interests to disclose.

## Authors' Contributions
KM and KO developed the idea. KM wrote analytical R code. etc etc. 

## Data Availability
The datasets generated during and/or analysed during the current study are available from the corresponding author on reasonable request.
